Area maximisation in continuous time

### 2013-11-22 Notes/ContTime.tex
minor update to notes
scaling mode and laplace bound

Using the same approach as the area bound, we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
\begin{aligned}
  \pdiff{\hat{A}(s)}{\W^\pm_{gh}}
     =&\, 2rf^\pm \eq_g \brk{ \sum_i a_i(s) (\fptb_{gi}(0)-\fptb_{hi}(0))
     +c_g(s) (\eta^+_g(s) - \eta^+_h(s)) } \\
     &\pm 2\eq_g (\eta^+_g(s) - \eta^+_h(s)).
\end{aligned}
\end{equation}
%
This is exactly the same as \eqref{eq:derivA}.
It follows that, using exactly the same perturbations, that the Laplace transform of the SNR curve for \emph{any} model is lower than that of a certain model with the serial topology having the same equilibrium distribution.

@@

This procedure can be iterated an arbitrary number of times
%
\begin{equation}\label{eq:bootiter}
  B_k(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_k(t_0),
  \qquad
  \env_{k+1}(t_0)=\frac{B_k(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_k'(s_0)}{B_k(s_0)}.
\end{equation}
%
This will end at the fixed point
%
\begin{equation}\label{eq:bootfixedpt}
  B_\infty(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_\infty(t_0),
  \qquad
  \env_\infty(t_0)=\frac{B_\infty(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_\infty'(s_0)}{B_\infty(s_0)}.
\end{equation}
%
We can eliminate $\env_\infty$ and $t_0$ (assuming that $s_0\to \infty$ as $t_0 \to 0$ and vice versa) to get the following integro-differential equation:
%
\begin{equation}\label{eq:bootbnd}
  B_\infty(s) = \intd[_0^\infty]{s_0} \e^{(s-s_0)B'_\infty(s_0)/B_\infty(s_0)} 
      \brk{B'_\infty(s_0)-\frac{B_\infty(s_0)B''_\infty(s_0)}{B'_\infty(s_0)}}.
\end{equation}
%

>>>>

Using the same approach as the area bound, we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
\begin{aligned}
  \pdiff{\hat{A}(s)}{\W^\pm_{gh}}
     =&\, 2rf^\pm \eq_g \brk{ \sum_i a_i(s) (\fptb_{gi}(0)-\fptb_{hi}(0))
     +c_g(s) (\eta^+_g(s) - \eta^+_h(s)) } \\
     &\pm 2\eq_g (\eta^+_g(s) - \eta^+_h(s)).
\end{aligned}
\end{equation}
%
This is exactly the same as \eqref{eq:derivA}.
Everything about the perturbation analysis carries over from the proof of the area bound, except for the \hyperref[sec:rescale]{scaling mode} that allowed us to ignore constraints \eqref{eq:Wmax}.
If we could find a way around this, It would follow, using exactly the same perturbations, that the Laplace transform of the SNR curve for \emph{any} model is lower than that of a certain model with the serial topology having the same equilibrium distribution.

In this case,
%
\begin{equation}\label{eq:scaleLaplace}
  \sum_\pm\sum_{ij} \W^\pm_{ij} \, \pdiff{A(s)}{\W^\pm_{ij}} = -s A'(s).
\end{equation}
%
The scaling mode essentially scales $s$ in the opposite direction.

@@

This procedure can be iterated an arbitrary number of times
%
\begin{equation}\label{eq:bootiter}
  B_k(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_k(t_0),
  \qquad
  \env_{k+1}(t_0)=\frac{B_k(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_k'(s_0)}{B_k(s_0)}.
\end{equation}
%
This will end at the fixed point
%
\begin{equation}\label{eq:bootfixedpt}
  B_\infty(s) = \intd[_0^\infty]{t_0} \e^{-st_0}\env_\infty(t_0),
  \qquad
  \env_\infty(t_0)=\frac{B_\infty(s_0) \e^{s_0t_0-1}}{t_0},
  \quad t_0 = -\frac{B_\infty'(s_0)}{B_\infty(s_0)}.
\end{equation}
%
We can eliminate $\env_\infty$ and $t_0$ (assuming that $s_0\to \infty$ as $t_0 \to 0$ and vice versa) to get the following integro-differential equation:
%
\begin{equation}\label{eq:bootbnd}
  B_\infty(s) = \intd[_0^\infty]{s_0} \e^{(s-s_0)B'_\infty(s_0)/B_\infty(s_0)-1}
      \brk{B'_\infty(s_0)-\frac{B_\infty(s_0)B''_\infty(s_0)}{B'_\infty(s_0)}}.
\end{equation}
%
